\documentclass[11pt, letterpaper]{article}

% import packages
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage[empty]{fullpage}
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\usepackage{enumitem}

% -------------------------------------------------------------------------------------------------------------------- %
% Imports commands from source files
\input{src/Header}
\input{src/GeneralHeading}
\input{src/ProjectHeading}
\input{src/CircleList}
\input{src/BulletList}
\input{src/EmptyList}
\input{src/PlainItem}
\input{src/BoldedItemAndDescription}

% -------------------------------------------------------------------------------------------------------------------- %
\pagestyle{fancy}
\fancyhf{}  % clear header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt} % removes header line
\renewcommand{\footrulewidth}{0pt} % removes footer line

\raggedbottom
\raggedright

\setlength{\tabcolsep}{0in}

% remove extra left margin
\addtolength{\oddsidemargin}{-0.5in}
% remove extra right margin
\addtolength{\evensidemargin}{-0.5in}
% extend text further right
\addtolength{\textwidth}{1in}
% remove extra top margin
\addtolength{\topmargin}{-0.5in}
% increase text height; required in order to make use of lower portion of the page
\addtolength{\textheight}{1in}

% generate correct unicode codepoints
\pdfgentounicode=1

% -------------------------------------------------------------------------------------------------------------------- %
% controls section's look
\titleformat{\section}{
    \vspace{-11pt} % controls space above section
    \scshape % gives text the title case with sizing dif between upper and lower case char
    \large % increases text size
}{}{
    0em % margin left for text
}{}[
    \color{black} % specifies line coloring
    \titlerule % adds hr line
    \vspace{-5pt} % removes extra top margin
]

% -------------------------------------------------------------------------------------------------------------------- %
\begin{document}

    % ---------------------------------------------------------------------------------------------------------------- %
    \rHeader{Trevor Busk}{trevor@tbusk.com}{tbusk.com}{+12695125088}{+1-269-512-5088}

    % ---------------------------------------------------------------------------------------------------------------- %
    \section{Education}

    \rGeneralHeading{Ferris State University}{Big Rapids, MI}{Bachelor of Science in Digital Media Software Engineering, GPA: 4.00}{May 2022 -- May 2026}

    % ---------------------------------------------------------------------------------------------------------------- %
    \section{Experience}

    \rGeneralHeading{Ferris State University}{Remote}{Research Assistant}{Jan 2026 -- Present}
    \rListBeginCircle
    \rPlainItem{Served as the sole developer for Ferrell, a custom LLM-powered VS Code extension designed to support students.}
    \rPlainItem{Built the application from scratch, connecting a modern webview frontend with React, TypeScript, and Tailwind CSS to a secure, Dockerized Java Spring Boot backend and PostgreSQL database hosted on AWS.}
    \rPlainItem{Presented the architecture and capabilities of Ferrell to a diverse audience as a featured speaker at Ferris AI Day.}
    \rListEndCircle

    \rGeneralHeading{Telic Corporation}{Remote}{Software Engineer}{Oct 2025 -- Present}
    \rListBeginCircle
        \rPlainItem{Created an ecommerce web platform using PayloadCMS, PostgreSQL, Docker, and Next.js to create products, manage content for the website, and procure personalized kids books via ML model integration and automation.}
        \rPlainItem{Researched and experimented with dozens of ML models and platforms to identify the most effective models at image generation, mixing, face-swapping, and feature alteration.}
        \rPlainItem{Implemented comprehensive i18n (English and Arabic) for international reach, and customized the PayloadCMS admin dashboard to streamline book creation and content management.}
    \rListEndCircle

    \rGeneralHeading{AD Solutions}{Remote}{Software Engineer}{June 2024 -- Present}
    \rListBeginCircle
    \rPlainItem{Owned the end-to-end project lifecycle after securing a solo contract, automating the entire software delivery process by architecting a multi-stage CI/CD pipeline with GitHub Actions for testing, Docker builds, and quick deployments.}
    \rPlainItem{Engineered a secure internal portal using React, TypeScript, and Bootstrap as well as a customer masquerade feature that reduced support resolution times.}
    \rPlainItem{Designed and implemented a new, normalized database schema from the ground up to enhance the platform scalability from the existing few thousand customers to much, much more.}
    \rPlainItem{Developed a high-performance payment automation that processes complex transactions across 20+ tables in-real-time, eliminating manual accounting intervention and saving dozens of hours per month.}
    \rPlainItem{Created automation tools for Sales, HR, and the CX team, including a customer onboarding system with automated email reminders, a batch account creation system, and a lead-tracking reporter, enhancing team velocity.}
    \rListEndCircle

    \rGeneralHeading{Kendall College of Art and Design}{Remote}{Software Engineer Intern}{Sept 2023 -- May 2024}
    \rListBeginCircle
    \rPlainItem{Engineered the core backend for an industry-first billing portal by designing a Spring Boot application with MariaDB database and integrating with a massive, undocumented ERP system by creating at least a dozen RESTful APIs.}
    \rPlainItem{Developed key frontend components using React and TypeScript, including secure login, payment, and autopay UIs, while also driving project velocity by managing the team's agile workflow and issue tracking on GitHub.}
    \rListEndCircle

    % ---------------------------------------------------------------------------------------------------------------- %
    \section{Projects}
    \rListBeginEmpty
%        \rBoldedItemAndDescription{Vala JetBrains IDE Plugin}{Authored and published an open-source language plugin for the Vala language.}
        \rBoldedItemAndDescription{Warehouse Item Classification}{Engineered a computer vision system to reduce military disposition waste.}
        \rBoldedItemAndDescription{Portfolio Website}{Created a portfolio website using Preact, TypeScript, TailwindCSS, and GitHub Pages.}
        \rBoldedItemAndDescription{LaTeX Résumé Template}{Created a modular LaTeX resume template which this résumé uses.}
        \rBoldedItemAndDescription{Remote Development Environment}{Setup and used a RDE on the cloud with Hetzner for a few months.}
%        \rBoldedItemAndDescription{Customer Support Chatbot}{Created a widget for websites using React, TailwindCSS, Spring Boot, and OpenAI.}
    \rListEndEmpty

    % ---------------------------------------------------------------------------------------------------------------- %
    \section{Open Source}

    \rProjectHeading{Vala JetBrains IDE Plugin}{github.com/vala-lang/vala-jetbrains}
    \rListBeginCircle
    \rPlainItem{Published plugin for JetBrains IDEs enabling development in the Vala programming language made in Java.}
    \rPlainItem{Implemented a variety of features using lsp including codelens, inline-docs, syntax checks, and more using LSP4IJ.}
    \rPlainItem{Added advanced syntax highlighting, vala-lint integration, new project wizard, formatter, and basic syntax checks.}
    \rListEndCircle

%    \rProjectHeading{Vala Docs}{github.com/vala-lang/vala-docs}
%    \rListBeginCircle
%        \rPlainItem{Ported static site generator from Sphinx to VitePress.}
%        \rPlainItem{Ported hundreds of documents from reStructuredText to Markdown.}
%        \rPlainItem{Added documentation on suffixes, data types, syntax, and resolved various issues.}
%    \rListEndCircle

%    \rProjectHeading{Monitor}{github.com/elementary/monitor}
%    \rListBeginCircle
%        \rPlainItem{Updated statusbar and indicator GPU usage to use most-active GPU on multi-GPU systems.}
%        \rPlainItem{Added swap usage and total info to system info memory graph.}
%        \rPlainItem{Tested per-process GPU usage and added support for AMD systems through working with the maintainer.}
%        \rPlainItem{Patched issue with CSV parsing of CPU information.}
%        \rPlainItem{Created CI/CD test runner GitHub Action.}
%    \rListEndCircle

%    \rProjectHeading{Settings-Power}{github.com/elementary/settings-power}
%    \rListBeginCircle
%        \rPlainItem{Patched battery-usage setting switch sizing issue.}
%    \rListEndCircle
%
%    \rProjectHeading{Appcenter Dashboard}{github.com/elementary/appcenter-dashboard}
%    \rListBeginCircle
%        \rPlainItem{Patched issue where content was cut off on mobile layouts.}
%    \rListEndCircle
%
%    \rProjectHeading{Screenshot}{github.com/elementary/screenshot}
%    \rListBeginCircle
%        \rPlainItem{Patched segfault issue where app crashed when the screenshot height was 1/4x or greater than the width.}
%    \rListEndCircle
%
%    \rProjectHeading{Greenmail}{github.com/greenmail-mail-test/greenmail}
%    \rListBeginCircle
%        \rPlainItem{Patched issue where duplicate messages were being delivered when cc and bcc share the same address as destination.}
%    \rListEndCircle

    % ---------------------------------------------------------------------------------------------------------------- %
    \section{Skills}

    % Shortened list containing only keywords to job
    \rListBeginEmpty
        \rBoldedItemAndDescription{Tech Stack}{Java, JavaScript, TypeScript, Python, Spring Boot, React, Docker, Git, TailwindCSS, AWS, GCP}
    \rListEndEmpty

    % expanded list containing all keywords from experience and projects
%    \rListBeginEmpty
%        \rBoldedItemAndDescription{Languages}{Java, JavaScript, TypeScript, Python, Vala}
%        \rBoldedItemAndDescription{Databases}{MariaDB, Microsoft SQL Server, PostgreSQL}
%        \rBoldedItemAndDescription{Frameworks}{Spring Boot, React, Preact, Thymeleaf, Freemarker, PayloadCMS, Quarkus, TailwindCSS, Bootstrap}
%        \rBoldedItemAndDescription{Tools}{Docker, GitHub, Git, Google Cloud, Linux, Hetzner, Figma, AWS}
%    \rListEndEmpty

\end{document}